A simulation-based assessment of the relation between Stone Age sites and relative sea-level change along the Norwegian Skagerrak coast

### 2022-09-23 analysis/paper/paper.Rmd
Setting up tiling of edited DTM to distribute with research compendium

@@

# Digital terrain model
dtm <- rast("/home/isak/phd/eaa_presentation/dtm10/dtm10.tif")

>>>>

```{r load_dtm, include = FALSE}
# This chunk tried to the load the edited DTM. Due to the file sizes involved
# this is not distributed with the repository but had to be assembled by running
# 03dtm_edit.R which compiles the original DTM stored in 400 tiles, edits this
# and stores the derived version in the derived data folder. This requires
# a local installation of GRASS GIS (see the script for more details).

# Digital terrain model
dtm <- rast(here("analysis/data/derived_data/dtm10.tif"))

@@
